Teaching

### 2025-09-17 ProjectBlog/paper2/SP2 Review Response/ReviewResponse.qmd

---
title: "Response Strategy for CIST and HICSS Feedback"
date: 12/23/2023
date-modified: last-modified
date-format: full
categories: [Paper2]
image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
bibliography: references.bib
---

::: panel-tabset
## CIST {#sec-dr.idris-adjerid}

### 2025-09-17 index.qmd
font palatino

<table style="width:100%">
  <tr>
    <td>Department of Business Information Technology</td>
    <td align="right">Tel: 540-824-8612</td>
  </tr>
  <tr>
    <td>Pamplin College of Business, Virginia Tech</td>
    <td align="right">Email: shaokang@vt.edu</td>
  </tr>
  <tr>
    <td>Blacksburg, VA 24061</td>
    <td align="right"><a href="https://wholehealth.isce.vt.edu/members-directory/yang-shaokang-bio.html">Whole Health Consortium</a></td>
  </tr>
</table>

>>>>

+-----------------------------------------------+-----------------------------------------------------------------------------------------------------+
| Department of Business Information Technology | Tel: 540-824-8612                                                                                   |
+-----------------------------------------------+-----------------------------------------------------------------------------------------------------+
| Pamplin College of Business, Virginia Tech    | Email: shaokang\@vt.edu                                                                             |
+-----------------------------------------------+-----------------------------------------------------------------------------------------------------+
| Blacksburg, VA 24061                          | [Whole Health Consortium](https://wholehealth.isce.vt.edu/members-directory/yang-shaokang-bio.html) |
+-----------------------------------------------+-----------------------------------------------------------------------------------------------------+

### 2025-09-17 posts/Clustering Anlysis/cluster.qmd
font palatino

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
df1 = df
df1[['sleep_debt','sleep_duration','screen_time','message','unlock','especiallyclose_m','family_m','friend_m','romantic_m','naps','naps_dur']].describe(percentiles=[.10,.15,.20,.25,.50,.55,.60,.65,.70, .75,.80,.85,.90,.95]).round(2)
```

@@

import pandas as pd
import matplotlib.pyplot as plt
from matplotlib.lines import Line2D

# Assuming df1 is already defined as df
df1 = df

# Data preparation steps (as per your instructions)
df1['screen_time_bin'] = None

# Creating bins as [0, 10), [10, 20), ...
bins = list(range(0, 190, 10))  # Define bins from 0 to 180 in steps of 10
labels = [f"[{bins[i]},{bins[i+1]})" for i in range(len(bins)-1)]  # Create labels like '[0,10)', '[10,20)', etc.

# Creating screen_time_bin column using pd.cut
df1['screen_time_bin'] = pd.cut(df1['screen_time'], bins=bins, labels=labels, right=False, include_lowest=True)

# Aggregating data for each bin
grouped = df1.groupby('screen_time_bin').agg({
    'sleep_debt': 'mean',
    'message': 'mean',
    'screen_time': 'count'
}).reset_index()

# Plotting
plt.rcParams['font.family'] = 'Times New Roman'
fig, ax1 = plt.subplots(figsize=(14, 8))

# Line plot for sleep debt trend
line1, = ax1.plot(grouped['screen_time_bin'], grouped['sleep_debt'], color='purple',
                  linestyle='-', marker='o', label='Sleep Debt')
for x, y in zip(grouped['screen_time_bin'], grouped['sleep_debt']):
    ax1.annotate(f'{y:.2f}', (x, y), textcoords="offset points", xytext=(0, 10), ha='center', color='purple')

# X and Y labels
ax1.set_xlabel('Screen Time (minutes)', fontsize=14, color='black')
ax1.set_ylabel('Sleep Debt (minutes)', fontsize=14, color='black')
ax1.tick_params(axis='x', rotation=30, labelcolor='black', labelsize=10)
ax1.tick_params(axis='y', labelcolor='black', labelsize=12)
# ax1.set_title('Sleep Debt, Screen Time and Message')

# Secondary axis for message count
ax2 = ax1.twinx()
line2, = ax2.plot(grouped['screen_time_bin'], grouped['message'], color='darkorange',
                  linestyle='-', marker='o', label='Message')
for i, txt in enumerate(grouped['message']):
    ax2.annotate(f'{txt:.2f}', (grouped['screen_time_bin'][i], grouped['message'][i]),
                 textcoords="offset points", xytext=(0, 10), ha='center', color='darkorange')
ax2.set_ylabel('Message', fontsize=14, color='black')
ax2.tick_params(axis='y', labelcolor='black', labelsize=12)

# Tertiary axis for bar plot of observations
ax3 = ax1.twinx()
bars = ax3.bar(grouped['screen_time_bin'], grouped['screen_time'], width=0.4, color='lightblue',
               alpha=0.3, label='Number of Observations')
ax3.spines['right'].set_position(('outward', 60))

# Hide the axis for Number of Observations
ax3.get_yaxis().set_visible(False)
ax3.spines['right'].set_visible(False)

# Draw connection lines from bar bottoms to the x-axis range
for bar, bin_label in zip(bars, grouped['screen_time_bin']):
    bar_x = bar.get_x() + bar.get_width() / 2
    bar_bottom = bar.get_y()
    ax1.add_line(Line2D([bar_x, bar_x], [bar_bottom, -10], color='gray', linestyle='-'))

for bar in bars:
    yval = bar.get_height()
    ax3.text(bar.get_x() + bar.get_width() / 2, yval, f'{int(yval)}', va='bottom', ha='center', color='black')

# Legend
lines = [line1, line2]
bars_proxy = plt.Line2D([0], [0], color='lightblue', alpha=0.3, lw=8)
labels = ['Sleep Debt', 'Message', 'Number of Observations']
fig.legend(lines + [bars_proxy], labels, loc='upper right', bbox_to_anchor=(0.96, 0.99), fontsize=12)

# Tight layout and save
fig.tight_layout()
plt.savefig('/Users/shaokangyang/Downloads/model-free.svg', format='svg', dpi=300)
plt.show()
```

### **Marginal effect estimates with multiplicative interaction models**

![](images/nonparametric%20rela.svg){fig-align="center"}

>>>>

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
df1 = df
df1[['sleep_debt','sleep_duration','screen_time','message','unlock','especiallyclose_m','family_m','friend_m','romantic_m','naps','naps_dur']].describe(percentiles=[.10,.15,.20,.25,.50,.55,.60,.65,.70, .75,.80,.85,.90,.95]).round(2)
```

@@

# Creating a special bin for 0
df1=df[df['screen_time']>15]
bins = [-np.inf, 0.001] + list(range(15, 185, 5))  # 0.1 to include 0 in the first bin exclusively
df1['screen_time_bin'] = pd.cut(df1['screen_time'], bins=bins, right=False, include_lowest=True)
# Recalculating the aggregated data
grouped = df1.groupby('screen_time_bin').agg({'sleep_debt':'mean', 'message':'mean', 'screen_time':'count'}).reset_index()
# Replotting with the adjusted bins
fig, ax1 = plt.subplots(figsize=(14, 8))
# Line plot for sleep debt trend
line1, = ax1.plot(grouped['screen_time_bin'].astype(str), grouped['sleep_debt'], color='blue', linestyle='-', marker='o', label='Sleep Debt')
# Adding labels for sleep debt
for x, y in zip(grouped['screen_time_bin'].astype(str), grouped['sleep_debt']):
    ax1.text(x, y, f'{y:.2f}', va='bottom', ha='center', color='blue')
# Setting the left y-axis for sleep debt
ax1.set_xlabel('Screen Time (minutes)')
ax1.set_ylabel('Average Sleep Debt')
ax1.set_title('Sleep Debt, Screen Time and Message')
ax1.tick_params(axis='x', rotation=45)
# Line plot for message count on a secondary y-axis
ax2 = ax1.twinx()
line2, = ax2.plot(grouped['screen_time_bin'].astype(str), grouped['message'], color='darkorange', linestyle='--', marker='o', label='Message')
# Adding labels for message count
for i, txt in enumerate(grouped['message']):
    ax2.annotate(f'{txt:.2f}', (grouped['screen_time_bin'].astype(str)[i], grouped['message'][i]), textcoords="offset points", xytext=(0,10), ha='center')
ax2.set_ylabel('Message')
# Bar plot for the number of observations on a secondary y-axis
ax3 = ax1.twinx()
bars = ax3.bar(grouped['screen_time_bin'].astype(str), grouped['screen_time'], width=0.4, color='lightgrey', alpha=0.5, label='Number of Observations')
ax3.spines['right'].set_position(('outward', 60))  # Offset the right spine of ax3
ax3.set_ylabel('Number of Observations')
# Labeling the number of observations above each bar
for bar in bars:
    yval = bar.get_height()
    ax3.text(bar.get_x() + bar.get_width() / 2, yval, f'{int(yval)}', va='bottom', ha='center', color='black')
# Adjusting the plot
ax1.grid(True, which='both', linestyle='--', linewidth=0.5)
ax2.grid(False)
ax3.grid(False)
# Adding legends
fig.legend(loc='upper right')
fig.tight_layout()
plt.show()
```

### 2025-09-17 research.qmd
font palatino

-   Topics: Policy evaluation on health IT, Digital technologies, Economics of AI
-   Methodologies: Causal inference with econometrics, machine learning, statistical learning

@@

### Policy Evaluation on Health IT

@@

-   **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.**\
    Shaokang Yang, Idris Adjerid
    -   Conference on Health IT and Analytics (CHITA) — Apr 2025, Austin, TX
    -   INFORMS Annual Meeting — Oct 2024, Seattle, WA
-   **Smartphone Use, Social Support, and Sleep Health.**\
    Shaokang Yang, Idris Adjerid
    -   Conference on Health IT and Analytics (CHITA) — May 2024, Washington, DC
    -   33rd Annual POMS Conference — May 2023, Orlando, FL
    -   Conference on Health IT and Analytics (CHITA) — May 2023, Washington, DC

>>>>

-   Topics: Public policy evaluation on health IT, Digital technologies, Economics of AI
-   Methodologies: Causal inference with econometrics, machine learning, statistical learning

@@

### Public policy Evaluation on Health IT

@@

- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* **Scheduled on INFORMS Annual Meeting (2:09 PM – 2:27 PM)**, Atlanta, GA, Oct 28, 2025.

- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Conference on Health IT and Analytics (CHITA)*, Austin, TX, Apr 2025.

- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Doctoral Consortium of CHITA*, Austin, TX, Apr 2025.

- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *INFORMS Annual Meeting*, Seattle, WA, Oct 2024.

- Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* *Conference on Health IT and Analytics (CHITA)*, Washington, DC, May 2024.

- Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* *33rd Annual POMS Conference*, Orlando, FL, May 2023.

- Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* *Conference on Health IT and Analytics (CHITA)*, Washington, DC, May 2023.

### 2025-09-17 teaching.qmd
job website
font palatino

>>>>

## Instructor

-   **BIT 3424 — Intro to Business Analytics Modelling** — Summer 2024

*Undergraduate advanced course; programming with VBA, Python, and R*

## Tutorial Instructor

-   **BIT 4624 — Cybersecurity Analytics**

Cybersecurity tutorials in data analytics and machine learning with R — Fall 2024

Cybersecurity tutorials in data analytics and machine learning with R — Spring 2023

Cybersecurity tutorials in data analytics and machine learning with R — Fall 2022
